---
name: Matthew Richard Voss
surname: Ross
position: > 
            Assistant Professor ESS; 
            
            Faculty Director, Geospatial Centroid
            
address: "Ecosystem Science and Sustainability, Colorado State University"
www: rossyndicate.com
twitter: magicalsystems
github: matthewross07
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::moderncv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tibble)
library(tidyverse)
library(scholar)
```



# Education

```{r}
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "BA Ecology, French Minor", "2006-2010", "University of Colorado", "Boulder, CO",
  "PhD Ecology", "2011-2017", "Duke University", "Durham, NC",
  "Post-Doc Remote Sensing", "2017-2018", "University of North Carolina", "Chapel Hill, NC"
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```


# Teaching 

**WR 418 (3 credits, 2018-2022)- Land-use and Water Quality -** Course covers basic aqueous geochemistry,
with an emphasis on analyzing data using R and open access datasets. Constructing
open access book [here](https://matthewrvross.com/wr418/land-use-and-water-quality-wr418.html)

**WR 419 (3 credits, 2018-2020) - Water Quality Analyses -** Course covers analytical tools for analyzing 
water quality data with an emphasis on maintaining and curating a sensor network.

**ESS 523a (3 credits, 2019-present) - Environmental Data Science Introduction -** Course covers environmental analysis
in R, with an emphasis on geospatial analysis and visualization. 

**ESS 523c (2 credits, 2022-present) - Environmental Data Science Applications - Water Resources - ** course covers detailed water resource analyses pipelines using R. 

**WR 204 (3 credits, 2023-present) - Sustainable Watersheds** - Course covers
introductory watershed and sustainability topics. Mostly delivering old material
in 2023, but hopeful to redesign in Fall 2023. 

**WR 440 (3 credits, 2022-present) - Watershed Problem Analysis** - Capstone course
for Watershed students. 

**Stat 158 A&B (1 credit, 2020) -**  Open access course for learning R [ Module 1](https://csu-r.github.io/Module1/), [Module 2](https://csu-r.github.io/Module2/)

**Open access hydrology course modules** [Link](https://openecodatalab.github.io/Hydrology-Online/)

**Shiny R Workshop** Course teaches students how to make shinyapps with all
students successfully producing apps after one week course [Link](https://www.nrel.colostate.edu/ecoacademy/rshiny/)

**Graduate Student Advisor of the Year** Ecosystem Science and Sustainability Department, 2019

**Award for Creative, Innovative and Impactful Instruction** Warner College of
Natural Resources, 2020

# Publications

```{r}
scholar::get_publications("FjuxZdYAAAAJ&hl") %>%
  mutate(author = gsub('MRV Ross','*MRV Ross*',author)) %>%
  detailed_entries(
    what = title,
    when = year,
    with = author,
    where = journal,
    why = cites
  ) %>% 
  arrange(when)

```



# Awarded Grants and Awards 

## **2023**

  - USGS Remote Sensing Branch, PI. *AquaSat 2.0 democratizing and improving remote sensing
  of water quality for inland waters* ($199,900). 


  - City of Fort Collins, PI. *Poudre River Monitoring Network and Decision System         
    (long-term funding)* ($50,000 per year in long-term city budget)


  - BHP Internet of Water, PI. *Visualizing and interpreting municipal water quality data* 
    ($350,000)

## **2022**

NASA Water Resources, PI. *Real-time satellite and sensor fusion for predicting and understanding water quality threats to water supply networks of Northern Colorado* ($451,000)


Northern Colorado Water Supplier Coalition, PI. *Cameron Peak Fire Water Quality impacts to Rivers and Reservoirs, towards a Decision Support System* ($86,000)

City of Fort Collins, PI. *Poudre River Monitoring Network and Decision System (extension)*
($12,000) 

NASA Remote Sensing of Water Quality, PI. *Understanding and predicting algae blooms in networks of rivers and reservoirs* ($606,000)

## **2021**


USGS Integrated Information Dissemination Division, PI. *Process-Guided Deep Learning for Informing Selection of Monitoring Locations in Priority Watersheds* ($199,253)

Colorado Water Center, PI. *High elevation fire controls on reservoir and river algae blooms* ($35,000)

Northern Colorado Water Supplier Coalition, PI. *Cameron Peak Fire Water Quality impacts to Rivers and Reservoirs* ($85,000)


## **2020**

NSF Hydrological Sciences RAPID Award, CSU PI. *Collaborative Research: Increased access to infrastructure for distance education in hydrologic science* ($20,552)

Colorado State University Provost Office, PI. *University-wide training in foundational data-analysis software* ($19,996)

Colorado Water Institute, PI. *Linking the topology of forest disturbance to water quality to enhance forest and water resource management in Colorado* ($49,970)

City of Fort Collins, PI. *Poudre River Monitoring Network and Decision System*
($12,000) 

## **2019**

NSF DEB Macrosystems and NEON-Enabled Science, CO-PI. *Collaborative Research:
MACRO-Sheds: Comparative Ecosystem Biogeochemistry at Continental Scales*
(Total: \$997,000 with Duke University, CSU Portion after chief data scientist moves from Duke to CSU (in 2022): $620,864)

USDA National Need Fellowship program, CO-PI. 
*Re-visioning graduate training for the era of agricultural big data*. Support for 4 Master's and 1 PhD student to get ag or watershed data
science degrees ($243,500)

NSF EAR Hydrological Sciences Post-DOC awarded directly to Anna Bergstrom. 
*Controls on weathering, solute fluxes, and geologic carbon cycling in 
glacierized catchments* Faculty advisor ($174,000).

Wyoming Water Research Program. Identifying, predicting and managing the occurrence of harmful cyanobacterial blooms in Wyoming reservoirs (CSU portion $25,200)


## **2018**

Partnership with the City of Fort Collins and In-Situ Sensor Manufacturing for 
a real-time water quality monitoring and decision network in the Poudre River
(Estimated in-kind contribution from the City and In-Situ: $85,000)

Colorado Water Institute, PI. *Tools for improving knowledge of reservoir water quality in the Front Range of Colorado* ($49,991) 


# Selected Presentations (2018-2023)

## **2022**

**MRV Ross** *From Dissonance to Harmony in big environmental datasets* Invited
Speaker at University of Nevada, Reno

**MRV Ross** *Remote sensing of water quality for management and science* Invited
Speaker at University of Florida, Gaineseville

A whole raft of student presentations that I am terrible at documenting. 


## **2021**

**MRV Ross** *Using Environmental Big Data to Understand, Manage, and Better Design Freshwater Ecosystems* Invited speaker to University of California Santa Barbara Bren School

## **2020**

**MRV Ross** *Matched-up, the importance of open-access training data for global-scale remote sensing of water quality* Invited speaker to the Workshop
on Knowledge Guided Machine Learning at University of Minnesota. 2020

**MRV Ross** *From printing press to pdfs, the limits of papers in scholarly communication and open science* Invited speaker to Virtual Summit on Incorporating Data Science and Open Science Techniques in Aquatic Research. 2020

SN Topp^, TM Pavelsky, EH Stanley, X Yang, CG Griffin, **MRV Ross.** *Multi-Decadal Increases in U.S. Lake Water Clarity* Invited Talk at Ecological Society of America Virtual Conference. 2020. 


## **2019**

J Gardner, **MRV Ross**, SN Topp, X Yang, TM Pavelsky. *Trends and patterns in riverine suspended sediment concentrations across the continental USA revealed by satellite remote sensing.*

X Yang, M Belanger, DK Byron, W Dolana, H Galit, S Januchowski-Hartley, M Jorrisen, T Langhorst, E Lawton, KA McQuillan, T Pavelsky, S Pawar, **MRV** Ross, A Whittemore. *Our fragmented rivers––mapping human-made river obstructions around the globe.*

SN Topp^, TM Pavelsky, **MRV Ross.**, EH Stanley, X Yang. *Lakes as integrators: Multi-decadal fluctuations in regional lake water clarity and seasonality across the U.S.* 

T Langhorst, TM Pavelsky, SN Topp, **MRV Ross**, C Dai, MT Durand, RPM Frasson, I Howat. *Remotely sensed discharge and sediment flux of the Sagavanirktok River.*

## **2018**

**MRV Ross**, SN Topp, AP Appling, X Yang, J Gardner, T Pavelsky.
*What can 34 years of imagery tell us about suspended sediment
dynamics and controls in large rivers?* Fall Meeting of the 
American Geophysical Union, Washington DC, December 2018.

**MRV Ross**. *The ecology of a designed ecosystem: legacies in the man-made mountains of Appalachia.* Invited speaker to 
CU-Boulder Ecology Symposium, 2018. 

**MRV Ross**. *Novel approaches to understanding spatial and temporal variation in water quality*. Invited speaker to CU-Boulder
Civil and Environmental Engineering Symposium. 2018