---
name: Matthew Richard Voss
surname: Ross
position: > 
            Assistant Professor ESS; 
            
            Faculty Director, Geospatial Centroid
            
address: "Ecosystem Science and Sustainability, Colorado State University"
www: rossyndicate.com
twitter: magicalsystems
github: rossyndicate
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::moderncv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tibble)
library(tidyverse)
library(scholar)
library(googlesheets4)
library(lubridate)
```



# Education

```{r}
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "BA Ecology, French Minor", "2006-2010", "University of Colorado", "Boulder, CO",
  "PhD Ecology", "2011-2017", "Duke University", "Durham, NC",
  "Post-Doc Remote Sensing", "2017-2018", "University of North Carolina", "Chapel Hill, NC"
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

<!-- # Teaching -->

<!-- ```{r, eval = F} -->
<!-- teach <- read_sheet('https://docs.google.com/spreadsheets/d/1XWfiUsNNslmVhfh3cPlZC7F8lMGWpbsPZCMSgnX9VF4/edit#gid=764505479', sheet = 'Teaching') -->



<!-- teach %>% -->
<!--   filter(!is.na(code)) %>% -->
<!--   mutate(test_title = paste0('\\href{',link,'}','{',title,'}')) %>% -->
<!--   detailed_entries( -->
<!--     what = test_title, -->
<!--     why = description, -->
<!--     when = sy, -->
<!--     with = code, -->
<!--     .protect = FALSE -->
<!--   )  -->

<!-- ``` -->


# Teaching 

**WR 418 (3 credits, 2018-2022)- Land-use and Water Quality ** Course covers basic aqueous geochemistry,
with an emphasis on analyzing data using R and open access datasets.

**WR 419 (3 credits, 2018-2020) - Water Quality Analyses ** Course covered analytical tools for analyzing 
water quality data with an emphasis on maintaining and curating a sensor network.

**ESS 523a (3 credits, 2019-present) - Environmental Data Science ** Course covers environmental analysis
in R, with an emphasis on geospatial analysis and visualization. 

**ESS 523c (2 credits, 2022-present) - Environmental Data Science   Water Resources  ** Course covers detailed water resource analyses pipelines using R. 

**WR 204 (3 credits, 2023-present) - Sustainable Watersheds**  Course covers
introductory watershed and sustainability topics. 

**WR 440 (3 credits, 2022-present) - Watershed Problem Analysis**  Capstone course
for Watershed students. 

**Stat 158 A&B (1 credit, 2020)  **  Open access course for learning R [ Module 1](https://csu-r.github.io/Module1/), [Module 2](https://csu-r.github.io/Module2/)

**Open access hydrology course modules** [Materials](https://rossyndicate.github.io/Hydrology-Online/)



# Awards

**Graduate Student Advisor of the Year** Ecosystem Science and Sustainability Department, 2019

**Award for Creative, Innovative and Impactful Instruction** Warner College of
Natural Resources, 2020

**Outstanding Reviewer** American Geophysical Union, Global Biogeochemical Cycles, 2020

**Dean’s Award for Excellence to an Early Career Faculty Member** Warner College of Natural Resources,
2022

# Major Service Contributions

- Faculty Director Geospatial Centroid (2020-present) - Coordinate and lead 
five full-time staff to deliver high quality geospatial
analyses, trainings, and workshops for clients both on and off campus. 

- Chair, Diversity Equity and Inclusion Committee for ESS Department (2022-present) 

- Faculty adviser for 15 Water Resource track Professional Science Masters Students (2021-present)

- Advised or Co-Advised 6 Research Masters Students, 3 PhD students

- Committee Member on 34 PhDs or Research MS



# Grants and Contracts 




```{r}
g <- read_sheet('https://docs.google.com/spreadsheets/d/1XWfiUsNNslmVhfh3cPlZC7F8lMGWpbsPZCMSgnX9VF4/edit#gid=764505479', sheet = 'Grants')


total_dollars = paste0('$',format(sum(g$total), big.mark = ','))
total_ross = paste0('$',format(sum(g$csu), big.mark = ','))


```

-   **Total Grants 2018 - `r year(Sys.time())` - `r total_dollars`**


-   **Portion to Lab 2018 - `r year(Sys.time())` - `r total_ross`**


## Individual Grants


```{r}

g %>%
  detailed_entries(
    what = funder,
    when = year,
    with = role,
    why = title,
    where = trimws(paste0('$',format((g$csu), big.mark = ',')))
  ) %>%
  arrange(-when)


```

$\linebreak[4]$

## Contracts to the Geospatial Centroid

The Geospatial Centroid is a service and contracting center at Colorado State University.
We specialize in geospatial analysis, undergraduate internship training, and
broad cartography.
In Winter of 2020, I transitioned into the role of Faculty Director of the Centroid. As a service
center on campus, we operate primarily with funds from external and internal
clients, below is a quick summary of our contract growth under my leadership. 

$\linebreak[2]$

- FY 21 - Total Contracts ~ $95,000
- FY 22 - Total Contracts ~ $185,000
- FY 23 - Total Contracts ~ $265,000
- FY 24 (as of Aug 2023) ~ $355,000


# Publications

```{r}
scholar::get_publications("FjuxZdYAAAAJ&hl") %>%
  detailed_entries(
    what = title,
    when = year,
    with = author,
    where = journal,
    why = cites
  ) %>% 
  arrange(-when)

```



# Press


```{r}
pr <- read_sheet('https://docs.google.com/spreadsheets/d/1XWfiUsNNslmVhfh3cPlZC7F8lMGWpbsPZCMSgnX9VF4/edit#gid=764505479', sheet = 'Press') %>%
 mutate(link_title = paste0('\\href{',link,'}','{',title,'}'))




pr %>%
  detailed_entries(
    what = link_title,
    when = year,
    where = publication,
    .protect = F
  ) %>% 
  arrange(-when)


```


# Data and code downloads

```{r}
d <- read_sheet('https://docs.google.com/spreadsheets/d/1XWfiUsNNslmVhfh3cPlZC7F8lMGWpbsPZCMSgnX9VF4/edit#gid=764505479', sheet = 'data')  %>%
 mutate(link_title = paste0('\\href{',link,'}','{',title,'}'))


d %>%
  detailed_entries(what = link_title,
                   when = year,
                   why = downloads,
                   .protect = F) %>%
  arrange(-when)


```



# Selected Presentations 

```{r}
p <- read_sheet('https://docs.google.com/spreadsheets/d/1XWfiUsNNslmVhfh3cPlZC7F8lMGWpbsPZCMSgnX9VF4/edit#gid=764505479', sheet = 'Presentations') 



p %>%
  detailed_entries(what = title,
                   where = where,
                   when = year,
                   with = authors) %>%
  arrange(-when)

```



