---
name: Matthew Richard Voss
surname: Ross
position: > 
            Assistant Professor ESS; 
            
            Faculty Director, Geospatial Centroid
            
address: "Ecosystem Science and Sustainability, Colorado State University"
www: rossyndicate.com
twitter: magicalsystems
github: matthewross07
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::moderncv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tibble)
library(tidyverse)
library(scholar)
library(googlesheets4)
library(lubridate)
```



# Education

```{r}
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "BA Ecology, French Minor", "2006-2010", "University of Colorado", "Boulder, CO",
  "PhD Ecology", "2011-2017", "Duke University", "Durham, NC",
  "Post-Doc Remote Sensing", "2017-2018", "University of North Carolina", "Chapel Hill, NC"
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

# Teaching

```{r, eval = F}
teach <- read_sheet('https://docs.google.com/spreadsheets/d/1XWfiUsNNslmVhfh3cPlZC7F8lMGWpbsPZCMSgnX9VF4/edit#gid=764505479', sheet = 'Teaching')



teach %>%
  filter(!is.na(code)) %>%
  mutate(test_title = paste0('\\href{',link,'}','{',title,'}')) %>%
  detailed_entries(
    what = test_title,
    why = description,
    when = sy,
    with = code,
    .protect = FALSE
  ) 

```


# Teaching 

**WR 418 (3 credits, 2018-2022)- Land-use and Water Quality -** Course covers basic aqueous geochemistry,
with an emphasis on analyzing data using R and open access datasets. Constructing
open access book [here](https://matthewrvross.com/wr418/land-use-and-water-quality-wr418.html)

**WR 419 (3 credits, 2018-2020) - Water Quality Analyses -** Course covers analytical tools for analyzing 
water quality data with an emphasis on maintaining and curating a sensor network.

**ESS 523a (3 credits, 2019-present) - Environmental Data Science Introduction -** Course covers environmental analysis
in R, with an emphasis on geospatial analysis and visualization. 

**ESS 523c (2 credits, 2022-present) - Environmental Data Science Applications - Water Resources - ** course covers detailed water resource analyses pipelines using R. 

**WR 204 (3 credits, 2023-present) - Sustainable Watersheds** - Course covers
introductory watershed and sustainability topics. Mostly delivering old material
in 2023, but hopeful to redesign in Fall 2023. 

**WR 440 (3 credits, 2022-present) - Watershed Problem Analysis** - Capstone course
for Watershed students. 

**Stat 158 A&B (1 credit, 2020) -**  Open access course for learning R [ Module 1](https://csu-r.github.io/Module1/), [Module 2](https://csu-r.github.io/Module2/)

**Open access hydrology course modules** [Link](https://openecodatalab.github.io/Hydrology-Online/)

**Shiny R Workshop** Course teaches students how to make shinyapps with all
students successfully producing apps after one week course [Link](https://www.nrel.colostate.edu/ecoacademy/rshiny/)

**Graduate Student Advisor of the Year** Ecosystem Science and Sustainability Department, 2019

**Award for Creative, Innovative and Impactful Instruction** Warner College of
Natural Resources, 2020

# Publications

```{r}
scholar::get_publications("FjuxZdYAAAAJ&hl") %>%
  mutate(author = gsub('MRV Ross','*MRV Ross*',author)) %>%
  detailed_entries(
    what = title,
    when = year,
    with = author,
    where = journal,
    why = cites
  ) %>% 
  arrange(-when)

```


# Awards




# Grants

## Totals 2018 - `r year(Sys.time())`


```{r}
g <- read_sheet('https://docs.google.com/spreadsheets/d/1XWfiUsNNslmVhfh3cPlZC7F8lMGWpbsPZCMSgnX9VF4/edit#gid=764505479', sheet = 'Grants')


total_dollars = paste0('$',format(sum(g$total), big.mark = ','))
total_ross = paste0('$',format(sum(g$csu), big.mark = ','))



```

-   **Total Grants 2018 - `r year(Sys.time())` - `r total_dollars`**


-   **Lab Portion 2018 - `r year(Sys.time())` = `r total_ross`**


## Individual Grants


```{r}

g %>%
  detailed_entries(
    what = funder,
    when = year,
    with = role,
    why = title,
  ) %>%
  arrange(-when)


```



# Selected Presentations (2018-2023)

```{r}

```



